Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-02-08 manuscript.Rmd
added missing package to packages.R; fixed typo in pre_process; wrote pca and pc plotting code

pca_data = rbind(subset(DAL, species == "Pinus"), 
        subset(TSK, species == "Pinus"), 
        subset(MFM, species == "Pinus"))

```

>>>>

pca_data = rbind(subset(DAL, species == "Pinus"), 
        subset(TSK, species == "Pinus"), 
        subset(MFM, species == "Pinus"))
pca_data[pca_data$treatment == "","treatment"] = "SPT"
pca_res = princomp(pca_data$sg2, scores = T)
scores =  as.data.frame(pca_res$scores[,1:10]) %>%
  mutate(ids = rownames(.), 
         core = pca_data$Label, 
         treatment = pca_data$treatment
         ) #%>%
  #melt(.,id.vars = "ids")
ggplot(scores, aes(Comp.1, Comp.2, color = core)) + geom_point()
# pca_data[scores[scores[,2] < -.2,"ids"]==pca_data$ids,1:10]
```
